NumPy---Array Programming in Python

### 2020-01-26 body.tex
Add Stefan's comments (from PR #48)

To facilitate \emph{interoperability}, the NumPy team has designed
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions (Fig.~\ref{fig:duck-arrays}).
NumPy, in turn, dispatches operations to the originating library, as required.
% FIXME: expand to 3 or more sentences discussing current efforts and
% issues with those, how did adoption go, what is being done next
%\url{https://numpy.org/neps/nep-0037-array-module.html}
Versions of these protocols have been successfully deployed.
% Ralf: Could you provide some proof of effectiveness, e.g., "This has made it
% possible to create distributed GPU arrays, enabling .... [find a reference to
% work by Peter Entschev]".

@@

Subclasses of NumPy often exist due to difficulty in constructing richer data
types, such as quantities with physical units \cite{astropy,Goldbaum2018,pint},
geometrical objects \cite{pygeos}, and missing numbers.
To improve \emph{extensibility}, we are currently overhauling the data type
system to make it easier to implement data types both in Python and C, and to
support these and other applications.

>>>>

To facilitate \emph{interoperability}, the NumPy team has designed
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions (Fig.~\ref{fig:duck-arrays}).
NumPy, in turn, dispatches operations to the originating library, as required.
% FIXME: expand to 3 or more sentences discussing current efforts and
% issues with those, how did adoption go, what is being done next
%\url{https://numpy.org/neps/nep-0037-array-module.html}
Versions of these protocols have been successfully deployed.
% Ralf: Could you provide some proof of effectiveness, e.g., "This has made it
% possible to create distributed GPU arrays, enabling .... [find a reference to
% work by Peter Entschev]".
% Below an attempt to start on this:
Thanks to these developments users of Dask and NumPy arrays are now capable
of scaling their computation to the GPU using Dask's CuPy integration with
only minimal code changes.
% spelled out on this page: https://docs.dask.org/en/latest/gpu.html
% The video cited embedded there could be a citation:i
% https://on-demand-gtc.gputechconf.com/gtcnew/sessionview.php?sessionName=s9198-dask+and+v100s+for+fast%2c+distributed+batch+scoring+of+computer+vision+workloads
However, general adoption has not yet been achieved mainly for compatibility
concerns.
% explain a bit what "compatibility concerns" means ...
Thus, we are actively addressing these concerns by revising and extending
these protocols with the aim of wide interoperability that spans the whole
scientific Python ecosystem up to and including domain libraries.

@@

Subclasses of NumPy often exist due to difficulty in constructing richer data
types, such as quantities with physical units \cite{astropy,Goldbaum2018,pint},
geometrical objects \cite{pygeos}, and missing numbers. % pandas: categoricals, IP addresses?
To improve \emph{extensibility}, we are currently overhauling the data type
system to make it easier to implement data types both in Python and C, and to
support these and other applications.
The widespread adoption of rich, user defined, data types can allow more
concise, feature rich scientific computing.
By making these user implemented data types a fundamental design of NumPy
these tools will enabled and interact naturally with different libraries.
% need to add a bit of clarity on what "enable and interact naturally with different libraries" means.
%
%  1. I expect multiple user dtypes can interact (naturally); 2. libraries such
%  as sklearn (or dask) might "just work" with e.g. physical Units (and
%  Categoricals, which they probably really would like to use e.g. for labels);
%  3. Things being inside a dtype rather than subclass is a better user
%  experience.
